Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
title

@@

\title{Type cones of $\b{g}$-vector fans}

@@

@@

\vincent{Link to \cref{sec:clusterCategories}.}
\vincent{\cref{lem:bijectionMeshMutations} might become a conjecture.}
\vincent{Pictures quivers.}

@@

We derive from \cref{prop:meshMutations} the following description of the facets of the type cone of the $\b{g}$-vector fan.

@@

%sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}, 'e3':{'e1':['c']}}, [('b','c')])
%
%sage: Q.non_kissing_fan().rays()
%N( 1,  0,  0),0
%N( 0,  0,  1),1
%N( 1,  0, -1),2
%N( 1, -1,  0),3
%N( 0,  0, -1),4
%N(-1,  0,  1),5
%N( 0, -1,  0),6
%N( 0, -1,  1),7
%N(-1,  0,  0),8
%N( 0,  1,  0),9
%N( 0,  1, -1)10
%in 3-d lattice N
%
%sage: TCNKC = type_cone_NKC(Q)
%sage: TCNKC
%A 11-dimensional polyhedron in QQ^11 defined as the convex hull of 1 vertex, 9 rays, 3 lines
%sage: TCNKC.lines()
%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
%sage: TCNKC.inequalities()
%(An inequality (0, 0, 0, 1, 0, 1, 0, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (-1, 0, 1, 0, 0, 0, 0, 0, 0, 1, -1) x + 0 >= 0,
% An inequality (1, 0, -1, 0, 1, 0, 0, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (1, -1, 0, -1, 0, 0, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 0, 0, 1, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 0, -1, -1, 1, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 1, -1, -1, 0, 1, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 0, 1, 0, 0, -1, -1, 1) x + 0 >= 0)
%sage: TCNKC.lines()
%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
\vincent{Todo}
\end{example}

@@

>>>>

% formating the part command
\makeatletter
\def\part{\@startsection{part}{1}%
\z@{.7\linespacing\@plus\linespacing}{.8\linespacing}%
{\LARGE\sffamily\centering}}
\@addtoreset{section}{part}
\makeatother
\renewcommand{\thesection}{\arabic{part}.\arabic{section}}

@@

\title[Generalized associahedra and minimal relations between $\b{g}$-vectors]{Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors}

@@

\part{Type cones of $\b{g}$-vector fans}

@@

\vincent{Link to \cref{sec:clusterCategories}.}
\vincent{\cref{lem:bijectionMeshMutations} might become a conjecture.}
\vincent{Pictures AR quivers + labeling of meshes reported on the inequalities.}

@@

We derive from \cref{prop:meshMutations} the following description of the facets of the type cone of the cluster fan.

@@

%sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}, 'e3':{'e1':['c']}}, [('b','c')])
%
%sage: Q.non_kissing_fan().rays()
%N( 1,  0,  0),0
%N( 0,  0,  1),1
%N( 1,  0, -1),2
%N( 1, -1,  0),3
%N( 0,  0, -1),4
%N(-1,  0,  1),5
%N( 0, -1,  0),6
%N( 0, -1,  1),7
%N(-1,  0,  0),8
%N( 0,  1,  0),9
%N( 0,  1, -1)10
%in 3-d lattice N
%
%sage: TCNKC = type_cone_NKC(Q)
%sage: TCNKC
%A 11-dimensional polyhedron in QQ^11 defined as the convex hull of 1 vertex, 9 rays, 3 lines
%sage: TCNKC.lines()
%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
%sage: TCNKC.inequalities()
%(An inequality (0, 0, 0, 1, 0, 1, 0, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (-1, 0, 1, 0, 0, 0, 0, 0, 0, 1, -1) x + 0 >= 0,
% An inequality (1, 0, -1, 0, 1, 0, 0, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (1, -1, 0, -1, 0, 0, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 0, 0, 1, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 0, -1, -1, 1, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 1, -1, -1, 0, 1, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 0, 1, 0, 0, -1, -1, 1) x + 0 >= 0)
%sage: TCNKC.lines()
%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
\vincent{Todo}
\vincent{Pictures AR quivers + labeling of meshes reported on the inequalities.}
\end{example}

@@

\part{Grothendieck group and relations between $\b{g}$-vectors}
